---
title: "Group 2 - Sleep and Effective Study"
author: "Student IDs: 500470817,500354333,500341470,500257148"
subtitle: "Project 1"
date: "University of Sydney | DATA1001 | March 2020"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

<br>

# Executive Summary
- The aim of this report is to ...
- The main discoveries are ...

<br>

# Full Report

## Initial Data Analysis (IDA)

The data for this project was collected via online survey distributed through social media (facebook etc) to peers and friends.

[Group 2, Project 1 Survey]
For ethical considerations, the anonymity of the responses from the participants were explicitly outlined at the beginning of the survey. Data was collected from 60 online respondents who all identified themselves as university students, thus this data is drawn from a sample of university students. The reliability of this data is restricted by some limitations including the method of distribution to friends and peers, which resulted in a small sample size and an over-representation of certain demographics in survey participation such as first year students, and 18 year old students. This selection bias evident in the collection of data for this project may have involved the confounding factor of age to our findings. While we aimed to get an accurate reflection of the university student population, this was restricted by our access to distribution platforms and was considered when drawing possible conclusions. The online survey involved a range of questions concerning the quality and quantity of both study and sleep within the students’ lifestyles. Initially, when the data was imported into R Studios, it was read as 11 variables with 60 rows of data and all of the variables were recognised as qualitative (character). However, with further inspection it was clear that the timestamps from the survey participants were registered as a variable and the variables of Age and SleepHrs needed to be changed from qualitative (categorical) into quantitative variables (numeric) to best suit our data analysis. Thus, we began our further data analysis with 10 variables (2 quant, 8 qual). Potential stakeholders and users of this data may include universities and other institutions invested in student wellbeing, to maximise student wellbeing and effectivity. 


```{r}
uni= read.csv("project.csv")

# Quick look at top 5 rows of data
head(`uni`)

## Size of data
dim(`uni`)

## R's classification of data
class(`uni`)

## R's classification of variables
str(`uni`)
table(`uni`$UniYear)


```

Summary:

- The data cames from [link](https://docs.google.com/forms/d/12-jOODOINI9kAE8_vXEeITjV18_mI0rCdspS3IveEzE/edit?ts=5e6834b6#responses)
- The data is/is not valid becaus
- Possible issues include ...
- Each row represents ...
- Each column represents ...

<br>

## What kind of sleeping patterns do university students have?

```{r}
Age=as.numeric(as.character(uni$age))
hist(Age,main='Histogram of Age',xlab='Age of respondents',ylab='Frequency',col='green')

b=table(uni$sleep_time)
barplot(b, main= "Hours of Sleep", ylab= "Frequency",xlab="Hours",col="pink")

library(ggplot2)
Sleep_time=uni$sleep_time

i=ggplot(uni,aes(Age,Sleep_time,colour= gender)) + geom_point()

library(plotly)
ggplotly(i)


```
Insert text and analysis. 
For the purposes of this project, sleeping patterns were measured by quantity and quality and this entailed collecting data about the hours of sleep and 
Summary: 

## Research Question 2

Insert text and analysis. 

Summary: 



# References (if needed)

Style: APA 

<br>


